---
title: "p8105_hw1_yx2507"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)

```
# problem 1

## making data frame

Create a data frame comprised of: a random sample of size 8 from a standard Normal distribution; a logical vector indicating whether elements of the sample are greater than 0; a character vector of length 8; a factor vector of length 8, with 3 different factor “levels”. Below shows the code and the result:

```{r}   
 problem_1=tibble(
   vec_numeric=rnorm(8),
   vec_logical=vec_numeric>0,
   vec_char=c("a","b","c","d","e","f","g","h"),
   vec_factor = factor(c("M","F","M","F","M","F","M","F"))

 ) 
#CHECK DATA FRAME
problem_1

```


## now take the mean
The result shows that numeric vairable and logical variable work while factor and character vairable can't get the mean.
```{r}
mean(problem_1$vec_numeric)
mean(problem_1$vec_logical)

```

```{r}
mean(problem_1$vec_char)
mean(problem_1$vec_fator)
```

## Conercion
Tn the below steps:
* convert the logical vector to numeric, and multiply the random sample by the result
* convert the logical vector to a factor, and multiply the random sample by the result
* convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result
```{r}
as.numeric(problem_1$vec_char)
as.numeric(problem_1$vec_logical)
as.numeric(problem_1$vec_factor)

```
coercision can change charactor vairable into N/A but can't convert to numeric variable. So it can't be calculated mean. While for logical variable, when converting to numerica vairables, "True" and "False" can be covert to 1 and 0 respectively. For factor variable, they can convert to the number indicating its level.

## multiply by random sample
```{r}
as.numeric(problem_1$vec_logical)*rnorm(8)
```

```{r}
as.factor(problem_1$vec_logical)*rnorm(8)
```

```{r}
as.numeric(as.factor(problem_1$vec_logical))*rnorm(8)
```

# Problem 2 Including Plots

## Create data frame

Create a data frame comprised of:
x: a random sample of size 500 from a standard Normal distribution
y: a random sample of size 500 from a standard Normal distribution
A logical vector indicating whether x + y > 1
A numeric vector created by coercing the above logical vector
A factor vector created by coercing the above logical vector

```{r}
set.seed(2)
  x=rnorm(500)
  y=rnorm(500)
  vec_logical_plot= x + y > 1
  vec_num = as.numeric(vec_logical_plot)
  vec_fact = as.factor(vec_logical_plot)
  
plot_df=tibble(x,y,vec_logical_plot,vec_fact,vec_num)

head(plot_df)

```

the number of rows in `plot_df` is `r nrow(plot_df)` columns is `r ncol(plot_df)`. The mean of x in the dataframe is `r mean(pull(plot_df, x))`. The median of the sample is `r median(pull(plot_df, x))`.The standard deviation of the sample is`r sd(pull(plot_df,x))` The proportion of x+y>1 is `r mean(pull(plot_df,x+y))`

## create scatterplot

color the logical vairable
```{r}
ggplot(plot_df, aes(x = x, y = y, color=vec_logical_plot)) + geom_point()

```
color the factor variable
```{r}
ggplot(plot_df, aes(x = x, y = y, color=vec_fact)) + geom_point()
```
colort the numeric varaible
```{r}
ggplot(plot_df, aes(x = x, y = y, color=vec_num)) + geom_point()
```


## export the this scatterplot


```{r}
ggsave("scatter_plot.pdf",height=4,width=6)

```


