---
title: "p8105_hw1_yx2507"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# R Markdown

## problem 1
-----------
creating a data frame

```{r}
library(tidyverse)

```
### making data frame
```{r}   
 problem_1=tibble(
   vec_numeric=rnorm(8),
   vec_logical=vec_numeric>0,
   vec_char=c("a","b","c","d","e","f","g","h"),
   vec_factor = factor(c("M","F","M","F","M","F","M","F"))

 ) 
#CHECK DATA FRAME
problem_1

```


now take the mean
```{r}
mean(problem_1$vec_numeric)
mean(problem_1$vec_logical)

```

numeric vairable and logical variable work

```{r}
mean(problem_1$vec_char)
mean(problem_1$vec_fator)
```

##convert chractor,logical and numeric variable into numeric
```{r}
as.numeric(problem_1$vec_char)
as.numeric(problem_1$vec_logical)
as.numeric(problem_1$vec_factor)

```
coercision can change charactor vairable into N/A but can't convert to numeric variable. So it can't be calculated mean. While for logical variable, when converting to numerica vairables, "True" and "False" can be covert to 1 and 0 respectively. For factor variable, they can convert to the number indicating its level.
