---
title: "p8105_hw1_yx2507"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# R Markdown

## problem 1
-----------
creating a data frame

```{r}
library(tidyverse)

```
### making data frame
```{r}   
 problem_1=tibble(
   vec_numeric=rnorm(8),
   vec_logical=vec_numeric>0,
   vec_char=c("a","b","c","d","e","f","g","h"),
   vec_factor = factor(c("M","F","M","F","M","F","M","F"))

 ) 
#CHECK DATA FRAME
problem_1

```


now take the mean
```{r}
mean(problem_1$vec_numeric)
mean(problem_1$vec_logical)

```

numeric vairable and logical variable work

```{r}
mean(problem_1$vec_char)
mean(problem_1$vec_fator)
```

##convert chractor,logical and numeric variable into numeric
```{r}
as.numeric(problem_1$vec_char)
as.numeric(problem_1$vec_logical)
as.numeric(problem_1$vec_factor)

```
coercision can change charactor vairable into N/A but can't convert to numeric variable. So it can't be calculated mean. While for logical variable, when converting to numerica vairables, "True" and "False" can be covert to 1 and 0 respectively. For factor variable, they can convert to the number indicating its level.

```{r}
as.numeric(problem_1$vec_logical)*rnorm(8)
```

```{r}
as.factor(problem_1$vec_logical)*rnorm(8)
```

```{r}
as.numeric(as.factor(problem_1$vec_logical))*rnorm(8)
```

## problem 2 Including Plots

Create a data frame comprised of:
x: a random sample of size 500 from a standard Normal distribution
y: a random sample of size 500 from a standard Normal distribution
A logical vector indicating whether x + y > 1
A numeric vector created by coercing the above logical vector
A factor vector created by coercing the above logical vector

```{r}
set.seed(2)
  x=rnorm(500)
  y=rnorm(500)
  vec_logical_plot= x + y > 1
  vec_num=as.numeric(vec_logical_plot)
  vec_fact=as.factor(vec_logical_plot)

  plot_df=tibble(x,y,vec_logical_plot,vec_fact,vec_num)

head(plot_df)

```

the number of rows in `plot_df` is `r nrow(plot_df)` columns is `r ncol(plot_df)`. The mean of x in the dataframe is `r mean(pull(plot_df, x))`. The median of the sample is `r median(pull(plot_df, x))`.The standard deviation of the sample is`r sd(pull(plot_df,x))` The proportion of x+y>1 is `r percent=(vec_num/(x+y))`
```{r}
ggplot(plot_df, aes(x = x, y = y, color=vec_logical_plot)) + geom_point()

```


### export the this scatterplot


```{r}
ggsave("scatter_plot.pdf",height=4,width=6)

```
