---
title: "P8105_hw1_yx2507"
output: github_document
---
## Yuqing Xue 9/18/2019

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r include=FALSE}

library(tidyverse)

```
# Problem 1

## Making data frame with different variable types

First, create a data frame comprised of: 
 *a random sample of size 8 from a standard Normal distribution; 
 *a logical vector indicating whether elements of the sample are greater than 0; 
 *a character vector of length 8; a factor vector of length 8, with 3 different factor “levels”. 
Below shows the code and the result:

```{r}
set.seed(1)
 problem_1 = tibble(
   vec_numeric=rnorm(8),
   vec_logical=vec_numeric>0,
   vec_char=c("a","b","c","d","e","f","g","h"),
   vec_factor = factor(c("M","F","M","F","M","F","M","F"))
 ) 
 
#CHECK DATA FRAME
problem_1

```
Data frame called problem_1 is created, containing four vairables: numeric varaiable"vec_numeric", logical variable"vec_logical", character variable"vec_char" and factor varaible called"vec_factor".

## Mean calculation
Try to take the mean of each varrable in the dataset problem_1. The `mean()`function works for numeric vairable `vec_numeric` and also works for logical variable`vec_logical`because it will convert `True`to 1 and `False ` to 0. Code and results are shown below:

```{r}
mean(problem_1$vec_numeric)

mean(problem_1$vec_logical)

```
When trying to calculate the mean for character variable "vec_char" and factor variable"vec_factor", warning shows up with N/A result. Mean function doesn't support these two variable types.
Code and results are shown below:

```{r}
mean(problem_1$vec_char)

mean(problem_1$vec_fator)
```

## Conercion
Use `as.numeric`to convert character, logical and factor variables into numeric varaibles, use `evel=false`to hide the result and show the code chunk.

Coercision can change charactor vairable into N/A but can't convert to numeric variable. So it can't be calculated mean. While for logical variable, when converting to numerica vairables, "True" and "False" can be covert to 1 and 0 respectively. For factor variable, they can convert to the number indicating its level.

```{r include=FALSE}
as.numeric(problem_1$vec_char)

as.numeric(problem_1$vec_logical)

as.numeric(problem_1$vec_factor)

```


## Multiply by random sample
In the below steps:
* convert the logical vector to numeric, and multiply the random sample by the result
* convert the logical vector to a factor, and multiply the random sample by the result
* convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result
Code and results are shown below:
When change type to numeric varaible, we can get the product after it multiply by a random sample:
```{r}
as.numeric(problem_1$vec_logical)*(problem_1$vec_numeric)
```
It's now meaningful to multiply a factor vairable which is converted from a logical variable to and random sample. N/A and warning sign shows up in the result.
```{r}
as.factor(problem_1$vec_logical)*(problem_1$vec_numeric)
```
But, after conver to a factor variable, it works after convert the factor varaible to a numeric vairable and then multiply a random sample.
```{r}
as.numeric(as.factor(problem_1$vec_logical))*(problem_1$vec_numeric)
```

# Problem 2 Including Plots

## Create data frame

Create a data frame comprised of:
x: a random sample of size 500 from a standard Normal distribution
y: a random sample of size 500 from a standard Normal distribution
A logical vector indicating whether x + y > 1
A numeric vector created by coercing the above logical vector
A factor vector created by coercing the above logical vector

```{r}
set.seed(1)
  x=rnorm(500)
  y=rnorm(500)
  vec_logical_plot= x + y > 1
  vec_num = as.numeric(vec_logical_plot)
  vec_fact = as.factor(vec_logical_plot)
  
plot_df=tibble(x,y,vec_logical_plot,vec_fact,vec_num)

head(plot_df)

```

The number of rows in `plot_df` is `r nrow(plot_df)` columns is `r ncol(plot_df)`. The mean of x in the dataframe is `r mean(pull(plot_df, x))`. The median of the sample is `r median(pull(plot_df, x))`.The standard deviation of the sample is`r sd(pull(plot_df,x))` The proportion of x+y>1 is `r mean(pull(plot_df,x+y))`

## Create scatterplot

Make a scatterplot of `y` and `x`, and color points using logical variable`vec_logical_plot`,factor variable `vec_fact ` and numeric variable` vec_num` separately.

1. color the logical vairable
```{r}
ggplot(plot_df, aes(x = x, y = y, color=vec_logical_plot)) + geom_point()

```

2. color the factor variable
```{r}
ggplot(plot_df, aes(x = x, y = y, color=vec_fact)) + geom_point()
```

3. colort the numeric varaible
```{r}
ggplot(plot_df, aes(x = x, y = y, color=vec_num)) + geom_point()
```

When the points are colored using nemeric variable, the color scale is shown as a continuous ranging from 0 to 1. If the points are colored by factor and logical varaible, the color scale will just show "false" and "true" regarding of the of color it used.

## Export the this scatterplot

Using `ggsave` to export the scatterplot to a pdf document named"scatter_plot.pdf".

```{r}
ggsave("scatter_plot.pdf",height=4,width=6)

```


